An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2023-11-21 article.tex
minor edits to styling

%\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
%\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC{} 0000 \sep{} 1111
%\end{keyword}
%%Research highlights
\begin{highlights}
 \item Highlight 1
 \item Highlight 2
 \item Highlight 3
 \item Highlight 4
\end{highlights}
\end{frontmatter}

@@

\subsection{Data}\label{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program. The program aims to support grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ Classes\end{tabular}} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6049 & 10 & \\
  Disease & Class & 6049 & 2 & \\
  Region & Class & 6049 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6049 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6049 & 16 & \\
  Area Harvested & Hectares & 6049 & & \\
  Electricity & Kilowatt Hours & 1014 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & \begin{tabular}[c]{@{}c@{}}Kilograms \\ of Nitrogen\end{tabular} & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6049 & 32 & \\
  Water Type & Class & 6049 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
The data originally contained only two multiclass variables: year and region. Related binary variables, such as the use of river water and the use of dam water, were combined to create a single multiclass variable. This was done by first converting each combination that occurred into a unique category (such as river and damn water used, as opposed to the two separate categories prior). These variables were then one-hot-encoded, changing each variable class into a binary value, with one indicating the presence of the class and zero indicating its absence. Further details about classes and their frequency is available in the appendices.
\par
The variable region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

@@

\subsection{cover crop types}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  Cover crop types & frequency \\ \midrule
  permanent_cover_crop_volunteer_sward & 1822 \\
  permanent_cover_crop_non_native & 936 \\
  permanent_cover_crop_native & 490 \\
  annual_cover_crop & 479 \\
  groundwater and surface water dam & 406 \\
  annual_cover_crop and permanent_cover_crop_volunteer_sward & 309 \\
  bare_soil & 225 \\
  permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 214 \\
  annual_cover_crop and permanent_cover_crop_non_native & 169 \\
  bare_soil and permanent_cover_crop_volunteer_sward & 129 \\
  bare_soil and permanent_cover_crop_non_native & 115 \\
  annual_cover_crop and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 101 \\
  bare_soil and annual_cover_crop & 93 \\
  permanent_cover_crop_native and permanent_cover_crop_volunteer_sward & 80 \\
  bare_soil and permanent_cover_crop_native & 78 \\
  annual_cover_crop and permanent_cover_crop_native & 78 \\
  permanent_cover_crop_native and permanent_cover_crop_non_native & 68 \\
  permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 44 \\
  annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 44 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_volunteer_sward & 33 \\
  bare_soil and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 26 \\
  annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_volunteer_sward & 17 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native & 15 \\
  annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native & 15 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_non_native & 13 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 12 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 11 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native & 8 \\
  bare_soil and permanent_cover_crop_native and permanent_cover_crop_non_native & 7 \\
  bare_soil and permanent_cover_crop_native and permanent_cover_crop_volunteer_sward & 6 \\
  bare_soil and permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 4 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_volunteer_sward and & 2 \\ \bottomrule
  \end{tabular}
  \end{table}

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  Irrigation type & frequency \\ \midrule
  dripper & 4800 \\
  dripper and non_irrigated & 342 \\
  Not listed & 319 \\
  dripper and overhead_sprinkler & 201 \\
  dripper and undervine_sprinkler & 91 \\
  non_irrigated & 65 \\
  undervine_sprinkler & 53 \\
  dripper and flood & 53 \\
  overhead_sprinkler & 46 \\
  dripper and overhead_sprinkler and undervine_sprinkler & 28 \\
  overhead_sprinkler and undervine_sprinkler & 12 \\
  dripper and non_irrigated and overhead_sprinkler & 11 \\
  flood and undervine_sprinkler & 10 \\
  dripper and flood and undervine_sprinkler & 7 \\
  dripper and flood and non_irrigated and overhead_sprinkler and undervine_sprinkler & 3 \\
  dripper and flood and overhead_sprinkler & 3 \\
  non_irrigated and undervine_sprinkler & 2 \\
  dripper and flood and non_irrigated & 1 \\
  dripper and non_irrigated and overhead_sprinkler and undervine_sprinkler & 1 \\
  flood and & 1 \\ \bottomrule
  \end{tabular}
  \end{table}

@@

  \subsection{year}
  % Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  data_year_id & frequency \\ \midrule
  2021/2022 & 954 \\
  2020/2021 & 860 \\
  2019/2020 & 599 \\
  2012/2013 & 590 \\
  2013/2014 & 549 \\
  2015/2016 & 548 \\
  2014/2015 & 505 \\
  2017/2018 & 493 \\
  2016/2017 & 485 \\
  2018/2019 & 466 \\ \bottomrule
  \end{tabular}
  \end{table}

>>>>

%\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
%\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC{} 0000 \sep{} 1111
%\end{keyword}
%%Research highlights
% \begin{highlights}
%  \item Highlight 1
%  \item Highlight 2
%  \item Highlight 3
%  \item Highlight 4
% \end{highlights}
\end{frontmatter}

@@

\subsection{Data}\label{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program. The program aims to support grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \small
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{Number of Classes} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6049 & 10 & \\
  Disease & Class & 6049 & 2 & \\
  Region & Class & 6049 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6049 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6049 & 16 & \\
  Area Harvested & Hectares & 6049 & & \\
  Electricity & Kilowatt Hours & 1014 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & KGs of Nitrogen & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6049 & 32 & \\
  Water Type & Class & 6049 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
\normalsize
The data originally contained only two multiclass variables: year and region. Related binary variables, such as the use of river water and the use of dam water, were combined to create a single multiclass variable. This was done by first converting each combination that occurred into a unique category (such as river and damn water used, as opposed to the two separate categories prior). These variables were then one-hot-encoded, changing each variable class into a binary value, with one indicating the presence of the class and zero indicating its absence. Further details about classes and their frequency is available in the appendices.
\par
The variable region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

@@

\subsection{cover crop types}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  Cover crop types & frequency \\ \midrule
  permanent cover crop volunteer sward & 1822 \\
  permanent cover crop non native & 936 \\
  permanent cover crop native & 490 \\
  annual cover crop & 479 \\
  groundwater and surface water dam & 406 \\
  annual cover crop and permanent cover crop volunteer sward & 309 \\
  bare soil & 225 \\
  permanent cover crop non native and permanent cover crop volunteer sward & 214 \\
  annual cover crop and permanent cover crop non native & 169 \\
  bare soil and permanent cover crop volunteer sward & 129 \\
  bare soil and permanent cover crop non native & 115 \\
  annual cover crop and permanent cover crop non native and permanent cover crop volunteer sward & 101 \\
  bare soil and annual cover crop & 93 \\
  permanent cover crop native and permanent cover crop volunteer sward & 80 \\
  bare soil and permanent cover crop native & 78 \\
  annual cover crop and permanent cover crop native & 78 \\
  permanent cover crop native and permanent cover crop non native & 68 \\
  permanent cover crop native and permanent cover crop non native and permanent cover crop volunteer sward & 44 \\
  annual cover crop and permanent cover crop native and permanent cover crop non native and permanent cover crop volunteer sward & 44 \\
  bare soil and annual cover crop and permanent cover crop volunteer sward & 33 \\
  bare soil and permanent cover crop non native and permanent cover crop volunteer sward & 26 \\
  annual cover crop and permanent cover crop native and permanent cover crop volunteer sward & 17 \\
  bare soil and annual cover crop and permanent cover crop native & 15 \\
  annual cover crop and permanent cover crop native and permanent cover crop non native & 15 \\
  bare soil and annual cover crop and permanent cover crop non native & 13 \\
  bare soil and annual cover crop and permanent cover crop native and permanent cover crop non native and permanent cover crop volunteer sward & 12 \\
  bare soil and annual cover crop and permanent cover crop non native and permanent cover crop volunteer sward & 11 \\
  bare soil and annual cover crop and permanent cover crop native and permanent cover crop non native & 8 \\
  bare soil and permanent cover crop native and permanent cover crop non native & 7 \\
  bare soil and permanent cover crop native and permanent cover crop volunteer sward & 6 \\
  bare soil and permanent cover crop native and permanent cover crop non native and permanent cover crop volunteer sward & 4 \\
  bare soil and annual cover crop and permanent cover crop native and permanent cover crop volunteer sward and & 2 \\ \bottomrule
  \end{tabular}
  \end{table}

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  Irrigation type & frequency \\ \midrule
  dripper & 4800 \\
  dripper and non irrigated & 342 \\
  Not listed & 319 \\
  dripper and overhead sprinkler & 201 \\
  dripper and undervine sprinkler & 91 \\
  non irrigated & 65 \\
  undervine sprinkler & 53 \\
  dripper and flood & 53 \\
  overhead sprinkler & 46 \\
  dripper and overhead sprinkler and undervine sprinkler & 28 \\
  overhead sprinkler and undervine sprinkler & 12 \\
  dripper and non irrigated and overhead sprinkler & 11 \\
  flood and undervine sprinkler & 10 \\
  dripper and flood and undervine sprinkler & 7 \\
  dripper and flood and non irrigated and overhead sprinkler and undervine sprinkler & 3 \\
  dripper and flood and overhead sprinkler & 3 \\
  non irrigated and undervine sprinkler & 2 \\
  dripper and flood and non irrigated & 1 \\
  dripper and non irrigated and overhead sprinkler and undervine sprinkler & 1 \\
  flood and & 1 \\ \bottomrule
  \end{tabular}
  \end{table}

@@

  \subsection{year}
  % Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  data year id & frequency \\ \midrule
  2021/2022 & 954 \\
  2020/2021 & 860 \\
  2019/2020 & 599 \\
  2012/2013 & 590 \\
  2013/2014 & 549 \\
  2015/2016 & 548 \\
  2014/2015 & 505 \\
  2017/2018 & 493 \\
  2016/2017 & 485 \\
  2018/2019 & 466 \\ \bottomrule
  \end{tabular}
  \end{table}
